% \section{Introduction}
% \label{sec:introduction}

\subsection{Purpose}
\label{ssec:purpose}

The LArSoft toolkit is designed to enable simulation, reconstruction and
physics analysis of data from any detection system based on Liquid Argon
TPCs. Its common tools and algorithms render the development and
analysis process more uniform across the Experiments. LArSoft is
extensible to accommodate evolving Experiments' needs and adoption by
new Experiments.

This document describes the current architecture of LArSoft toolkit.
The architecture was developed according to, and therefore reflects,
the consensus of LArSoft partners, including the adopting Experiments.

The document provides a reference for the reader interested in learning
the general structure of LArSoft, its functional areas and interactions
with the execution environment.
It also offers guidelines for the contributor aiming to develop new algorithms
within LArSoft or to use it together with external tools.


\subsection{Scope}
\label{ssec:scope}

This document provides an overview of the architecture of LArSoft
toolkit, including its relationship with the surrounding software
environment. The internal flow of the different subsystems is also
described. The document intends to capture and convey the significant
architectural decisions which have been made on the system, that reflect
into the current implementation or drive its development.\\

This document describes the architecture of LArSoft to date. It includes
description of the communication protocols with libraries it relies on
and with packages LArSoft cooperates with. The design and flow of
different components is described.

Some commonly used LArSoft elements are employed to exemplify
flows and connections, but this is no attempt to exhaustively describe
each, or any, of the single elements.

